---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# specmine

<!-- badges: start -->
```{r, echo = FALSE, results = 'asis'}
cat(
  badge_cran_release("specmine", "green")
)
```
<!-- badges: end -->

*specmine* is an R package for metabolomics and spectral data analysis.
It provides methods for data import, preprocessing, visualization,
univariate and multivariate analysis, machine learning, feature
selection, and pathway analysis.

Project repository:
<https://github.com/PedroFontao/specmine>

This package suggests `cyjShiny`, which is available from CRAN.
If needed, the development version can also be installed from GitHub:

```{r}
install.packages("cyjShiny")
# or
remotes::install_github("cytoscape/cyjShiny", ref = "master", build_vignettes = TRUE)
```

Installation
Install the released version from CRAN:
```{r}
install.packages("specmine")
```
Install the development version from GitHub:
```{r}
# install.packages("devtools")
devtools::install_github("PedroFontao/specmine")
```
Example
Load the package:
```{r}
library(specmine)
```
